---
title: "Designing a survey around fishery-dependent data"
subtitle: "FISH 507B project proposal"
author: John Best
bibliography: fish507b.bib
output:
    xaringan::moon_reader:
        lib_dir: libs
        nature:
            highlightStyle: github
            countIncrementalSlides: false
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = "center",
                      fig.height = 6,
                      dev = "svg")
```

# Fishery-dependent data in indices of abundance

- Catchability
- Preferential sampling

---

## A spatial abundance process

```{r}
knitr::include_graphics("figs/gp.svg")
```

---

## Observing the abundance process

```{r}
knitr::include_graphics("figs/25_robs_gp.svg")
```

---

## 25 preferential observations

```{r}
knitr::include_graphics("figs/25_obs_gp.svg")
```

---

## 50 preferential observations

```{r}
knitr::include_graphics("figs/50_obs_gp.svg")
```

---

## 25 preferential, 5 gridded observations

```{r}
knitr::include_graphics("figs/5_grid_gp.svg")
```

---


## 25 preferential, 10 gridded observations

```{r}
knitr::include_graphics("figs/10_grid_gp.svg")
```

---

## 25 preferential, 5 counter-preferential observations

```{r}
knitr::include_graphics("figs/5_counter_gp.svg")
```

---

## 25 prefernetial, 10 counter-preferential observations

```{r}
knitr::include_graphics("figs/10_counter_gp.svg")
```

---

# Practical issues

- In two dimensions

- Need to estimate catchability differences

- More complicated observation model
